MSTK: Mesh Toolkit, v 1.3 - DRAFT

### 2004-07-28 docs/MSTK.tex
Updated documentation for version 1.3

>>>>

\item[]\textbf{\textit{int} MESH\_DelInterior(\textit{Mesh\_ptr}
    mesh):} Delete the interior of a mesh and retain only its
    boundaries (including interior boundaries). For solid meshes, this
    results in a surface mesh (i.e., all mesh regions, and  mesh
    faces, edges and vertices classified on model regions are deleted). For
    surface meshes, this results in curve mesh. For an edge mesh, only
    the end vertices are retained (unlikely to be used this
    way). Undefined for a vertex mesh.
